---
title: "Content analysis"
author: "Jae Yeon Kim"
output:
html_document: 
  toc: true
  theme: united
---

## 0. Setup 

```{r}

# Clean up the environment

rm(list = ls())

# Import libraries (adapted from this link: https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # for the tidyverse framework
        irr, # for calculating inter-coder reliability scores
        vcd, # for kappa statistics 
        corrplot, # for visualizing correlation coefficients
        ggpubr, # for arranging ggplots   
        ggthemes, # for fancy ggplot themes
        gmodels, # quick summaries 
        patchwork # for arranging ggplots 
)

source("/home/jae/content-analysis-for-evaluating-ML-performances/functions/theme_publications.r")
theme_set(theme_Publication(14))

source("/home/jae/content-analysis-for-evaluating-ML-performances/functions/text_analysis.r")
```

## 1. Importing files 


```{r include=FALSE}

# Training data for classifying articles from Asian American newspapers 
training_asian <- read_csv("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/training_asian.csv") %>%
  dplyr::select(-contains("Notes")) %>%
  mutate(linked_progress_gran = ifelse(Promoting_collective_gains_A + Promoting_collective_gains_B >= 1, 1, 0),
         linked_hurt_gran = ifelse(Preventing_collective_losses_A + Preventing_collective_losses_B >= 1, 1, 0),
         linked_progress = ifelse(Promoting_collective_gains_A + Promoting_collective_gains_B == 2, 1, 0),
         linked_hurt = ifelse(Preventing_collective_losses_A + Preventing_collective_losses_B == 2, 1, 0))

# Training data for classifying articles from African American newspapers
training_black <- read_csv("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/training_black.csv") %>%
  dplyr::select(-contains("Notes")) %>%
  mutate(linked_progress_gran = ifelse(Promoting_collective_gains_A + Promoting_collective_gains_B >= 1, 1, 0),
         linked_hurt_gran = ifelse(Preventing_collective_losses_A + Preventing_collective_losses_B >= 1, 1, 0),
         linked_progress = ifelse(Promoting_collective_gains_A + Promoting_collective_gains_B == 2, 1, 0),
         linked_hurt = ifelse(Preventing_collective_losses_A + Preventing_collective_losses_B == 2, 1, 0))

# Dimensions 
dim(training_asian)
dim(training_black)

# Rename variables
names(training_asian) == names(training_black)

```

## 2. Descriptive statistics 

### 2.1. Merging

```{r}

# Wrangling 

df <- bind_rows(
  mutate(training_asian, group = "Asian Americans"),
  mutate(training_black, group = "African Americans"))

```

#### 2.2. 1. Class balance 

```{r}

ggarrange(
df %>%              
  group_by(group, linked_progress) %>%
  add_count() %>%
  ggplot(aes(x = as.factor(group), y = n, fill = as.factor(linked_progress))) +
    geom_col(position = "dodge", color="black") +
    scale_fill_manual(name = "Label", labels = c("No", "Yes"), values=c("red","blue")) +
    geom_text(aes(label = n), position=position_dodge(width=0.9), vjust=-0.25) +
    labs(x = "Group", y = "Frequency",
         title = "Linked progress",
         fill = "Group"),

df %>%
  group_by(group, linked_hurt) %>%
  add_count() %>%
  ggplot(aes(x = as.factor(group), y = n, fill = as.factor(linked_hurt))) +
    geom_col(position = "dodge", color="black") +     
    scale_fill_manual(name = "Label", labels = c("No", "Yes"), values=c("red","blue")) +
    geom_text(aes(label = n), position=position_dodge(width=0.9), vjust=-0.25) +
    labs(x = "Group", y = "Frequency",
         title = "Linked hurt",
         fill = "Group"), common.legend = TRUE)

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/content_analysis_n_count.png", height = 7, width = 10)
```

## 3. Analyzing Inter-coder agreement (percentage) and reliability scores

### 3.1. Percent agreement 

```{r}

# Extract percent agreement 

extract_percent_agreement <- function(data){
  # Calculatign the percent agreement 
  test <- agree(data, tolerance = 0) %>% as.numeric()
  # Extracting the number
  percent_agreement <- test[5]
  # Return the number
  percent_agreement
}

# Calculate the percent agreements and then put them with the other information into a dataframe 
df_agree <- data.frame("percent_agreement" = c(
extract_percent_agreement(subset(df, group = "Asian Americans")[,c(3,6)]),
extract_percent_agreement(subset(df, group = "Asian Americans")[,c(4,7)]),
extract_percent_agreement(subset(df, group != "Asian Americans")[,c(3,6)]),
extract_percent_agreement(subset(df, group != "Asian Americans")[,c(4,7)])),
           "type" = c("Linked progress", "Linked hurt", "Linked progress", "Linked hurt"),
           "group" = c(rep("Asian Americans", 2), rep("African Americans", 2)))
           
# Visualize 
df_agree %>%
  mutate(percent_agreement = round(percent_agreement, 0)) %>%
  ggplot(aes(x = group, y = percent_agreement/100, fill = type)) +
  geom_col(position = "dodge", color="black") +
  geom_text(aes(label = paste(percent_agreement, "%")), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(title = "Percentage agreement",
       y = "Agreement rate",
       x = "Group",
       fill = "Type") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
  scale_fill_manual(name = "Type", labels = c("Linked hurt", "Linekd progress"), values=c("red","blue")) 

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/content_analysis_agreement.png", height = 7)



```

### 3.2. Kappa statistics 

### 3.2.1. Original
 
```{r}

# Extract kappa statistics 

extract_kappa <- function(data){
  # Calculatign the kappa statistic 
  test <- Kappa(table(data))
  
  # Extracting the kappa statistic
  kappa <- test$Unweighted[1] %>% as.numeric()
  
  # Extracting confidence intervals
  lwr <- confint(test)[1,1]
  upr <- confint(test)[1,2]

  # Return the number
  data.frame("kappa" = kappa, 
                "lwr" = lwr, 
                "upr" = upr)}

df_kappa <- rbind(extract_kappa(subset(df, group = "Asian Americans")[,c(3,6)]),
      extract_kappa(subset(df, group = "Asian Americans")[,c(4,7)]),
      extract_kappa(subset(df, group != "Asian Americans")[,c(3,6)]),
      extract_kappa(subset(df, group != "Asian Americans")[,c(4,7)]))

df_kappa$type <- c("Linked progress", "Linked hurt", "Linked progress", "Linked hurt")

df_kappa$group <- c(rep("Asian Americans", 2), rep("African Americans", 2))
           
# Visualize 

df_kappa_plot <- df_kappa %>%
  mutate(kappa = round(kappa, 2)) %>%
  ggplot(aes(x = group, y = kappa, color = type)) +
  geom_pointrange(aes(ymax = upr, ymin = lwr)) +
  geom_text(aes(label = kappa), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(title = "Inter-coder reliability test",
       subtitle = "Including all topics",
       y = "Kappa coefficient",
       x = "Group",
       fill = "Type") +
  scale_color_manual(name = "Type", labels = c("Linked hurt", "Linekd progress"), values=c("red","blue")) +
  coord_flip() +
  ylim(c(0,1))

```

### 3.2.2. Original

The `Negate` trick comes from [this stackoverflow post](https://stackoverflow.com/questions/5831794/opposite-of-in).

```{r}

'%ni%' <- Negate('%in%')

dfn <- df %>%
  filter(Topics_C %ni% c("Mismatch", "Others", "Arts", "Recipes", "OTHERS", "Articles in Spanish", "Christian advice"))

dfn_kappa <- rbind(extract_kappa(subset(dfn, group = "Asian Americans")[,c(3,6)]),
      extract_kappa(subset(dfn, group = "Asian Americans")[,c(4,7)]),
      extract_kappa(subset(dfn, group != "Asian Americans")[,c(3,6)]),
      extract_kappa(subset(dfn, group != "Asian Americans")[,c(4,7)]))

dfn_kappa$type <- c("Linked progress", "Linked hurt", "Linked progress", "Linked hurt")

dfn_kappa$group <- c(rep("Asian Americans", 2), rep("African Americans", 2))
           
# Visualize 

dfn_kappa_plot <- dfn_kappa %>%
  mutate(kappa = round(kappa, 2)) %>%
  ggplot(aes(x = group, y = kappa, color = type)) +
  geom_pointrange(aes(ymax = upr, ymin = lwr)) +
  geom_text(aes(label = kappa), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(title = "",
       subtitle = "Excluding non-political topics",
       y = "Kappa coefficient",
       x = "Group",
       fill = "Type") +
  scale_color_manual(name = "Type", labels = c("Linked hurt", "Linekd progress"), values=c("red","blue")) +
  coord_flip() +
  ylim(c(0,1))

df_kappa_plot + dfn_kappa_plot

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/content_analysis_kappa_comp.png", width = 10, height = 7)

```

### 3.3. Exporting the summaries   

```{r}

irr_summary <- merge(df_agree, df_kappa)

irr_summary <- irr_summary %>%
  mutate(percent_agreement = percent_agreement / 100)

write.csv(irr_summary, "/home/jae/content-analysis-for-evaluating-ML-performances/processed_data/irr_summary.csv") 

```

## 4. Additional exploratory data analyses 

### 4.1. Construct validity test

```{r}

# Asian Americans
train_asian_plot <- bind_rows(mutate(training_asian %>%
  rename(Linked_progress = linked_progress) %>%
  rename(Linked_hurt = linked_hurt) %>%
  gather("linked_fate", "value", Linked_progress, Linked_hurt) %>%
  filter(value == 1) %>%
  filter(Topics_C != "Mismatch") %>%
  filter(Topics_C != "Others") %>%
  group_by(linked_fate) %>%
  count(Topics_C) %>%
  spread(linked_fate, n) %>%
  mutate(Linked_progress = ifelse(is.na(Linked_progress), 0, Linked_progress),
         Linked_hurt = ifelse(is.na(Linked_hurt), 0, Linked_hurt)) %>%
  mutate(difference = Linked_progress - Linked_hurt), Measurement = "Maximum"),
                              
  mutate(training_asian %>%
  rename(Linked_progress = linked_progress_gran) %>%
  rename(Linked_hurt = linked_hurt_gran) %>%
  gather("linked_fate", "value", Linked_progress, Linked_hurt) %>%
  filter(value == 1) %>%
  filter(Topics_C != "Mismatch") %>%
  filter(Topics_C != "Others") %>%
  group_by(linked_fate) %>%
  count(Topics_C) %>%
  spread(linked_fate, n) %>%
  mutate(Linked_progress = ifelse(is.na(Linked_progress), 0, Linked_progress),
         Linked_hurt = ifelse(is.na(Linked_hurt), 0, Linked_hurt)) %>%
  mutate(difference = Linked_progress - Linked_hurt), Measurement = "Minimum"))

# African Americans 
train_black_plot <- bind_rows(mutate(training_black %>%
  rename(Linked_progress = linked_progress) %>%
  rename(Linked_hurt = linked_hurt) %>%
  gather("linked_fate", "value", Linked_progress, Linked_hurt) %>%
  filter(value == 1) %>%
  filter(Topics_C != "Mismatch") %>%
  filter(Topics_C != "Others") %>%
  group_by(linked_fate) %>%
  count(Topics_C) %>%
  spread(linked_fate, n) %>%
  mutate(Linked_progress = ifelse(is.na(Linked_progress), 0, Linked_progress),
         Linked_hurt = ifelse(is.na(Linked_hurt), 0, Linked_hurt)) %>%
  mutate(difference = Linked_progress - Linked_hurt), Measurement = "Maximum"),
                              
  mutate(training_black %>%
  rename(Linked_progress = linked_progress_gran) %>%
  rename(Linked_hurt = linked_hurt_gran) %>%
  gather("linked_fate", "value", Linked_progress, Linked_hurt) %>%
  filter(value == 1) %>%
  filter(Topics_C != "Mismatch") %>%
  filter(Topics_C != "Others") %>%
  group_by(linked_fate) %>%
  count(Topics_C) %>%
  spread(linked_fate, n) %>%
  mutate(Linked_progress = ifelse(is.na(Linked_progress), 0, Linked_progress),
         Linked_hurt = ifelse(is.na(Linked_hurt), 0, Linked_hurt)) %>%
  mutate(difference = Linked_progress - Linked_hurt), Measurement = "Minimum"))

# Visualize 

ggarrange(
train_asian_plot %>%
  ggplot(aes(x = fct_reorder(Topics_C, difference), y = difference, fill = Measurement)) +
    geom_col(position = "dodge", color="black") +
    coord_flip() +
    labs(x = "Topics", y = "N of Linked progress - N of Linked hurt", title = "Asian Americans") +
    scale_fill_manual(name = "Measurement", labels = c("Maximum","Minimum"), values=c("red","blue")),

train_black_plot %>%
  ggplot(aes(x = fct_reorder(Topics_C, difference), y = difference, fill = Measurement)) +
    geom_col(position = "dodge", color="black") +
    coord_flip() +
    labs(x = "Topics", y = "N of Linked progress - N of Linked hurt", title = "African Americans") +
    scale_fill_manual(name = "Measurement", labels = c("Maximum","Minimum"), values=c("red","blue")), common.legend = TRUE)

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/content_analysis_topics_gran.png", width = 13, height = 7)

```

### 4.2. Visualizing correlation coefficients between the two concepts

```{r}

df %>%
  select(linked_progress, linked_hurt, group) %>%
  group_by(group) %>%
  summarize(corr = cor(linked_progress, linked_hurt), method = "Pearson") %>%
  mutate(corr = round(corr, 2)) %>%
  ggplot(aes(x = fct_reorder(group, corr), y = corr)) +
    geom_col() +
    labs(title = "Correlation Coefficients",
         subtitle = "Maximum",
         y = "Pearson Correlation coefficient",
         x = "Group",
         caption = "Ethnic NewsWatch") +
    geom_text(aes(label = corr)) 

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/corr_analysis.png")

df %>%
  select(linked_progress_gran, linked_hurt_gran, group) %>%
  group_by(group) %>%
  summarize(corr = cor(linked_progress_gran, linked_hurt_gran), method = "Pearson") %>%
  mutate(corr = round(corr, 2)) %>%
  ggplot(aes(x = fct_reorder(group, corr), y = corr)) +
    geom_col() +
    labs(title = "Correlation coefficients",
         subtitle = "Minimum",
         y = "Pearson correlation coefficient",
         x = "Group",
         caption = "Ethnic NewsWatch") +
    geom_text(aes(label = corr)) 

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/corr_analysis_gran.png")
```


## 5. Reading texts 

- Merging the text files with the content analysis 

```{r}

sample_asian <- read_rds("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/sample_asian.rds")
sample_black <- read_rds("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/sample_black.rds")

sample_asian <- bind_cols(sample_asian, training_asian %>% select(linked_progress, linked_hurt, linked_progress_gran, linked_hurt_gran, Topics_C))
sample_black <- bind_cols(sample_black, training_black %>% select(linked_progress, linked_hurt, linked_progress_gran, linked_hurt_gran, Topics_C))

```

- Comparing 100% and 50% data 

```{r}

# Merge 

df <- bind_rows(mutate(sample_asian, group = "Asian Americans"),
          mutate(sample_black, group = "African Americans"))

# Select 

df <- df %>% select(source, year, group, linked_progress, linked_progress_gran, 
              linked_hurt, linked_hurt_gran)

# Mutate 

df <- df %>% 
  mutate(lp_exclusive = ifelse(linked_progress == 1 & linked_hurt == 0, 1, 0),
         lh_exclusive = ifelse(linked_progress == 0 & linked_hurt == 1, 1, 0),
         lf_mixed = ifelse(linked_progress == 1 & linked_hurt == 1, 1, 0)) %>%
  mutate(lp_exclusive_gran = ifelse(linked_progress_gran == 1 & linked_hurt_gran == 0, 1, 0),
         lh_exclusive_gran= ifelse(linked_progress_gran == 0 & linked_hurt_gran == 1, 1, 0),
         lf_mixed_gran = ifelse(linked_progress_gran == 1 & linked_hurt_gran == 1, 1, 0))

# Remove numbers and special characters in the source titles 

df$source <- gsub('[[:digit:]]', '', df$source) 
df$source <- gsub('[[:punct:]]+', '', df$source) %>% trimws()

```

- Non-excluded 

```{r}

# Gather, group by and summary, and mutate

df$group <- factor(df$group, levels = c("Asian Americans", "African Americans"))

df_source <- df %>% 
  gather(linked_fate, value, c(lp_exclusive, lh_exclusive, lf_mixed, lp_exclusive_gran, lh_exclusive_gran, lf_mixed_gran)) %>%
  group_by(linked_fate, group) %>%
  summarize_content()

# Create two additional columns for sorting 

df_source$type <- ifelse(str_detect(df_source$linked_fate, "gran"), "Minimum", "Maximum")
df_source$linked_fate <- str_replace(df_source$linked_fate, "_gran", "")

# Visualize 

plot_ext_cases <- df_source %>%
 filter(linked_fate != "lf_mixed") %>%
 mutate(mean = round(mean, 2)) %>%
 ggplot(aes(x = fct_reorder(type, mean), y = mean, fill = linked_fate)) +
    geom_bar(stat="identity", color="black", 
             position=position_dodge()) +
    geom_errorbar(aes(ymin= lower.ci, ymax = upper.ci), width=.2,
                  position=position_dodge(.9)) +
    scale_fill_manual(name = "Type", labels = c("Linked hurt","Linked progress"), values=c("red","blue")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
    geom_text(aes(label = paste(mean*100, "%")),
              position=position_dodge(width=0.9), vjust=-0.25) +
    labs(y = "Proportion", x = "Threshold") +
    facet_wrap(~group)

  plot_ext_cases

ggsave("/home/jae/content-analysis-for-evaluating-ML-performances/outputs/content_data_sources_sub.png", width = 10, height = 6)

```

## 6. Exporting non-duplicated files 

```{r}

# Non-duplicated 
sample_asian <- sample_asian[!duplicated(sample_asian$text),]
sample_black <- sample_black[!duplicated(sample_black$text),]

# Check 
1008 - nrow(sample_asian)
1008 - nrow(sample_black)

# Export 
write.csv(sample_asian, "/home/jae/content-analysis-for-evaluating-ML-performances/processed_data/sample_asian.csv")
write.csv(sample_black, "/home/jae/content-analysis-for-evaluating-ML-performances/processed_data/sample_black.csv")

```

