---
title: "Content analysis"
author: "Jae Yeon Kim"
output:
html_document: 
  toc: true
  theme: united
---

## 0. Setup 

I tweaked the global option of the R Markdown to enlarge figures produced by ggplot2.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, 
                      echo = FALSE, warning = FALSE, message = FALSE) # global setting for enlarging image size
```

```{r}

# Clean up the environment

# rm(list = ls())

# Import libraries (adapted from this link: https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # for the tidyverse framework
        irr, # for calculating inter-coder reliability score
        ggthemes # for fancy ggplot themes
)

```

## 1. Importing files 


```{r}

# Training data for classifying articles from Asian American newspapers (dropping article identifiers)
training_asian <- read_csv("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/training_asian.csv")[, -1]

# Training data for classifying articles from African American newspapers (dropping article identifiers)
training_black <- read_csv("/home/jae/content-analysis-for-evaluating-ML-performances/raw_data/training_black.csv")[, -1]

# Dimensions 
dim(training_asian)
dim(training_black)

# Variable names
names(training_asian) == names(training_black)

```

## 2. Descriptive statisics 

### 2.1. Data cleaning 

```{r}

# Checking NAs

mean(is.na(training_asian))
mean(is.na(training_black))

# Replacing NAs with 0s

training_asian[is.na(training_asian)] <- 0

```

### 2.2. Data visualization 

```{r}

summary_statistics <- bind_rows(
  mutate(training_asian, Group = "Asian Americans"),
  mutate(training_black, Group = "African Americans ")
) %>%
  mutate(linked_progress = ifelse(Promoting_collective_gains_A == Promoting_collective_gains_B, 1, 0),
         linked_hurt = ifelse(Preventing_collective_losses_A == Preventing_collective_losses_B, 1, 0),
         topic = ifelse(Topics_A == Topics_B, Topics_A, NA))

summary_statistics %>%
  gather(type, value, linked_progress, linked_hurt) %>%
  group_by(Group, type) %>%
  summarise(mean = mean(value), # summarize mean, standard deviation, and n 
            sd = sd(value),
            n = n()) %>%
  mutate(se = sd / sqrt(n), # calculate standard errors and confidence intervals 
         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  ggplot(aes(x = reorder(type, mean), y = mean, ymax = upper.ci, ymin = lower.ci, col = Group)) +
    geom_pointrange(size = 0.7) + # point estimates plus confidence intervals 
    theme_fivethirtyeight() +
    coord_flip() +
    labs(y= "Percentages of Agreement", x = "Measure Type",
         title = "Percentages of Agreement",
         subtitle = "1: Perfect agreement, 0: Zero agreement",
         caption = "Ethnic NewsWatch") +
    theme(text = element_text(size = 15)) # large font size 

```

### 2,3, Checking the data balance 

```{r}
summary_statistics %>%
  group_by(Group, linked_progress) %>%
  summarize(n = n()) %>%
  mutate(freq = n / sum(n)) 

summary_statistics %>%
  group_by(Group, linked_hurt) %>%
  summarize(n = n()) %>%
  mutate(freq = n / sum(n)) 
```


## 3. Analyzing Inter-coder agreement (percentage) and reliability scores

### 3.1. Creating fuctions 

aggreement = accuracy 

precision = kappa 

http://web2.cs.columbia.edu/~julia/courses/CS6998/Interrater_agreement.Kappa_statistic.pdf

https://stats.stackexchange.com/questions/82162/cohens-kappa-in-plain-english

```{r}

extract_kappa <- function(data){
  
 kappa_progress  <- data %>%
      dplyr::select(contains("gains")) %>%
      kappa2("squared")
 
 kappa_hurt <- data %>%
      dplyr::select(contains("losses")) %>%
      kappa2("squared")
 
 data.frame("kappa_progress" = kappa_progress$value, 
            "kappa_hurt" = kappa_hurt$value)
}

extract_agreement <- function(data){
  
 agreement_progress  <- data %>%
      dplyr::select(contains("gains")) %>%
      agree()
 
 agreement_hurt <- data %>%
      dplyr::select(contains("losses")) %>%
      agree()
 
 data.frame("agreement_progress" = agreement_progress$value/100, 
            "agreement_hurt" = agreement_hurt$value/100)
}

```

### 3.2. Applying the functions to each group 

```{r}

irr_summary <- bind_rows(
mutate(bind_cols(training_asian %>%
  extract_kappa(),
          training_asian %>%
  extract_agreement()), Group = "Asian Americans"),
mutate(bind_cols(training_black %>%
  extract_kappa(),
          training_black %>%
  extract_agreement()), Group = "African Americans"))

```

### 3.3 Visualizing agreement and Kappa  

```{r}

irr_summary %>%
  gather(type, value, kappa_progress:agreement_hurt) %>% 
  ggplot(aes(x = reorder(as.factor(type), value), y = value, fill = Group)) +
    geom_col(position = "dodge") +
    coord_flip() +
    labs(y= "Intercorder Reliability Scores", x = "Linked Fate Type",
         title = "Content Analysis Results",
         subtitle = "Kappa = Cohen's Kappa. Inter-coder reliability score.",
         caption = "Ethnic NewsWatch") +
    theme_fivethirtyeight() + # five thirty eight theme 
    theme(text = element_text(size = 15)) # large font size 

```
